Online Updating of Variational Bayes for Heterogenous Forecasts of Vehicle Trajectory

### 2018-02-14 Cars/paper.tex
added split by variances

\title{Online Updating of Variational Bayes for Forecasts of Vehicle Trajectory with Heterogeneous Driver Behaviour}
\begin{document}
\maketitle
\section{Introduction}

@@

\item Including heterogeneity in the model will allow more dangerous vehicles to be identified, for example, 'lead-footed' drivers can have a larger variance on their acceleration.

@@

\item Compare Bayes MAP point estimates to a neural network and naive models
\item Error Metric: Euclidean Distance from predicted position to actual position
\item Compare log scores from streaming and standard VB forecast densities to see how the updating method compares to standard VB. I am also using MCMC, so we can compare either VB method to this, theoretically MCMC $\geq$ VB Standard $\geq$ VB Updating

@@

\begin{itemize}
\item 4071 vehicles are available in the sample
\item 500 are used to estimate splines and straighten the road to relative coordinates as described in Section 2
\item 2000 are used to train any models used
\item 1571 are available for testing
\item Each second (10 observations) models are fit to the sample of $z_{N+1, 1:T}$ and forecasts of $z_{N+1, T+1:T+30}$ are made, corresponding to a three second forecast horizon
\item Forecasts are compared in terms of predictive log-score (where a predictive density is available) and Euclidean error.
\end{itemize}

>>>>

\title{Online Updating of Variational Bayes for Heterogenous Forecasts of Vehicle Trajectory}
\begin{document}
\maketitle
\section{Introduction}

@@

\item Including heterogeneity in the model will allow the model to better adapt to drivers with more extreme behaviours, for example 'lead-footed' drivers can be assigned a larger variance on their acceleration while forecasts for more consistent drivers will benefit from a low variance.

@@

\item Show that a homogenous time series model has strong predictive performance compared to constant models / neural networks while also providing density forecasts.
\item Build a heterogenous version of the homogenous model, show that the density forecasts improve. 
\item Show that the Updating VB required to implement the heterogenous model in real time is comparable to MCMC and standard VB.

@@

Summary:
\begin{itemize}
\item The homogenous time series model has a significantly lower MAP error than other models
\item The heterogenous time series models have a similar MAP error to the homogenous model - the maximum of the forecast distribution is in a similar place.
\item The logscores for the heterogenous models are generally greater than the homogenous model indicating there is less uncertainty in the forecast distribution
 \item Updating VB has a similar logscore to MCMC across all priors
 \item Priors don't really matter too much
 \item The high precision in the homogenous posterior does make it better than the heterogenous models in small samples.
 \item Performance between homogenous and heterogenous becomes a tradeoff between high precision / biased mean vs. low precision, more accurate mean in the posterior.
 \item The heterogenous is sufficiently precise to outperform the homogenous model in terms of logscores after $T = 100$ (ten seconds).
 \item Most of the differences are due to the posterior of the variance parameters
 \item The homogenous model has a large variance for both variables, greater than $80\%$ and $92\%$ of heterogenous variances for acceleration and angle respectively.
 \item This is likely caused by a few drivers with high variance skewing the results in the homogenous model.
 \item The heterogenous model allows consistent drivers to have a low variance, and it performs very well in this case.
 \item Heterogenous models being able to assign a high variance allows more erratic / risky drivers to be identified.
 \end{itemize}

\begin{itemize}
\item 3873 vehicles are available in the sample
\item 500 are used to estimate splines and straighten the road to relative coordinates as described in Section 2
\item 2000 are used to train any models used
\item 1373 are available for testing
\item Each second (10 observations) models are fit to the sample of $z_{N+1, 1:T}$ and forecasts of $z_{N+1, T+1:T+30}$ are made, corresponding to a three second forecast horizon
\item Forecasts are compared in terms of predictive log-score (where a predictive density is available) and Euclidean error.
\end{itemize}
